\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

The set of test-cases that we are going to illustrate starts with an elementary case in an homogeneous domain. The aim of this test-case is to verify that the numerical model is actually working in different simulation/scenarios starting from the basic ones. But one step before that, is to verify the existence of cross flow in the following domain as this is defined in fig. \ref{fig:simple_case}. Fluid $1$ is introduced on the  across the left hand side of the formation. Later different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied.

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
\caption{This is the simple case where the initially piston shape front is collapsing and starts forming fingers, in a domain with uniform permeability.}
\label{fig:simple_case}
\end{center}
\end{figure}

One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}. A square shape formation consisted of$4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas). The aspect ratio of the domain is $1$ and is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied, meaning there is no mass transport in and out of the domain. The left hand side of the domain is defined as the inlet for fluid $1$ with a velocity of $u=1$ while the right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the formation is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and develops. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.

\begin{figure}
\begin{center}
\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
\caption{This is the first test-case of a square region with four subregions of constant permeabilities K. The mesh is unstructured but fixed and on average there are 5000 elements. Fluid $1$ is introduced from the right hand side at a constant velocity of u = 1, while as the flow progress the velocity magnitude drops to zero close to the outlet. This is a cross flow example based on the experimental work of \citet{evans_1994}. The main finger desrcibes the cross flow and starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary.}
\label{fig:square}
\end{center}
\end{figure}

In this test-case above the two phase volume volume fractions have the same but opposite behaviour across the length of the formation. From that point till the end of the formation, the velocity magnitute of the injected fluid remains the same having the minimum value since there is no more fluid 2 to be displaced. There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further since at the same time, as can been seen from the graph plot at fig. \ref{fig:square}, the phase volume fraction is constant.

The initial and boundary condition regarding the inlet and outlet are the same. One more test-case (fig.\ref{fig:testcase}), to verify the finger formation in a simple but same set-up is also illustrated.

\begin{figure}[h]
\begin{center}
\subfigure[MR1 fixed mesh start aspect ratio 2]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_1.pdf}
}%
\subfigure[MR1 fixed mesh end aspect ratio 2]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}\\
\end{center}
\caption{In this tes-case fixed and unstructured mesh is used. The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious. Simulation time step increases from left (a) to right (b) and from t=250(start) to t=3000(end).}
\label{fig:testcase}
\end{figure}

 The purpose is to expand this technique and introduce it into more complex formations so as to test it and develop a more stable and solid approach in real time and scale problems. A more detailed description of the element type and the formation that will be used in the next set of test cases follows.

>>>>

The set of test-cases that we are going to illustrate starts with an elementary case in an homogeneous domain. The aim of this test-case is to verify that the numerical model is actually working in different simulation/scenarios starting from the basic ones. One step before it is important to verify the existence of cross flow in the following domain as this is defined in fig. \ref{fig:simple_case}. Fluid $1$ is introduced on the  across the left hand side of the formation. Later different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied.

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (on average 3000 elements).}
\label{fig:simple_case}
\end{center}
\end{figure}

One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}. A square shape formation consisted of $4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas). The aspect ratio of the domain is $1$ and is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied, that at a solid boundary, the fluid will have zero velocity relative to the boundary. The fluid velocity at all fluid–solid boundaries is equal to that of the solid boundary.. The left hand side of the domain is defined as the inlet for fluid $1$ with a velocity of $u=1$ while the right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the formation is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and develops. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.

\begin{figure}[h]
\begin{center}
\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
\caption{This is the first test-case of a square region with four subregions of constant permeabilities K. The mesh is unstructured but fixed and on average there are 5000 elements. Fluid $1$ is introduced from the right hand side at a constant velocity of u = 1, while as the flow progress the velocity magnitude drops to zero close to the outlet. This is a cross flow example based on the experimental work of \citet{evans_1994}. The main finger desrcibes the cross flow and starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary.}
\label{fig:square}
\end{center}
\end{figure}

In this test-case above the two phase volume volume fractions have the same but opposite behaviour across the length of the formation. The velocity magnitute is builded up starting from the inlet all the way to the middle of the square. There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further (see fig.\ref{fig:square}) while the phase volume fraction is constant. An slightly modified test-case follows with the initial and boundary condition to remain the same, but in this set of simulations the geometrical aspect ration is $2$.

\begin{figure}[h]
\begin{center}
\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf}\label{a}}
\subfigure[flow at t=250]{\includegraphics[width=0.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}\label{b}}
\subfigure[flow at t=3000]{\includegraphics[width=0.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{b}}
\caption{In this test-case fixed and unstructured mesh is used. The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious. Simulation time step increases from left (a) to right (b) and from t=250(start) to t=3000(end).}
\label{fig:testcase}
\end{center}
\end{figure}

 The purpose of these case was to verify that our model is working for cases that experimentally are proven. This will allow to proceed further and expand this technique into more complex formations. A more detailed description of the element type and the formation that will be used in the next set of test cases follows.

\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}
